### 2014-04-15 doc/uist14/iteration1.tex
refining iteration 1, half way done.

\section{Iteration 1: IR vs. List}
Our system design uses IR as the beam cursor for physical target acqusition because the area coarse selection filters out the targets outside of the user's view range. This help during the fine selection time because there is a smaller set of targets to select from. The opposite is to have a complete list of all targets when there is no coarse selection and the disambiguation is always needed. This brought up the first question that we asked ourselves -- {\em how much does using IR help in reducing the selection time}. To answer that question and quantify the benefit of having IR for the coarse selection, we carried out our first target acquisition study which compares the {\em IR selection} and {\em list selection}.

@@

Our results indicate that {\em IR selection} is generally better than {\em list selection}. From Figure~\ref{fig:selection-time}A, the average target acquisition time for {\em IR selection} is 6.67 seconds, while for {\em list selection} it took 8.86 seconds. We run Student's t-test on the data and it shows significant difference ($t(279)=-3.81, p=0.00017$).

@@

To further generalize the results, in Figure~\ref{fig:time-vs-list-order}, we show the acquisition time for each individual target in {\em list selection} condition, ordered by their relative position in the list. Since with IR technique, the acquisition time is invariant from each target's order, we use solid lines to represent the average performance of {\em IR selection}. From this figure, we can see that once the target's order is larger than 6, the average acquistion time will be larger than the case when disambiguation is needed in {\em IR selection}. Therefore, we argue that once there are more targets in the physical space, the {\em list selection} method is not scalable.

>>>>

\section{Iteration 1: IR vs. List}
\subsection{Problem Statement and Goal}
Our system design uses IR as the beam cursor for physical target acquisition because the area coarse selection filters out the targets outside of the user's view range. This help during the fine selection time because there is a smaller set of targets to select from. The opposite is to have a complete list of all targets when there is no coarse selection and the disambiguation is always needed. This brought up the first question that we asked ourselves -- {\em how much does using IR help in reducing the selection time}. To answer that question and quantify the benefit of having IR for the coarse selection, we carried out our first target acquisition study which compares the {\em IR selection} and {\em list selection}.

\subsection{Technique}

@@

\subsection{Evaluation}
Our results indicate that {\em IR selection} is generally better than {\em list selection}. From Figure~\ref{fig:selection-time}A, the average target acquisition time for {\em IR selection} is 6.67 seconds, while for {\em list selection} it took 8.86 seconds. We run Student's t-test on the data and it shows significant difference ($t(279)=-3.81, p=0.00017$).

@@

To further generalize the results, in Figure~\ref{fig:time-vs-list-order}, we show the acquisition time for each individual target in {\em list selection} condition, ordered by their relative position in the list. Since with IR technique, the acquisition time is invariant from each target's order, we use solid lines to represent the average performance of {\em IR selection}. From this figure, we can see that once the target's order is larger than 6, the average acquistion time will be larger than the case when disambiguation is needed in {\em IR selection}. Therefore, we argue that once there are more targets in the physical space, the {\em list selection} method is not scalable. Further more, in real-life scenarios, targets would have longer names than an alphabet letter. This would increase the searching and text comparison time and also reduce the number of targets being shown in the UI screen.
